\subsection{Development Methods}

The development of the project is developed using two well known development methods in the
software industry, which is \textit{Agile development methodology} and \textit{DevOps deployment methodology}
Those methods was adapted after the first Software Development Life Cycle was applied.
The first step. Agile development methodology was used because it focus strongly on user experience
and input. This make the software high responsive to changes while developing the software and also
get the system up and factional quickly to meet the user needs. DevOps deployment methodology was to make
sure that I get the application up and running quick, using things such as continues deliverance, git and github.

\subsubsection{\textit{Planning}}

The first step on the development of the livestock monitoring system was to draft steps and
calculating labor cost and material costs, creating timetable with target goals and creating a
structure that can be followed when developing the system


\subsubsection{\textit{Creating}}

On this stage I focus more on packing the ESP32 to the case, connect the ESP to the WI-FI,
carefully soldering the system components on the veroboard, ensuring neat circuit is built and the are
no short circuit that may cause blowing of the components

\subsubsection{\textit{Developing}}

At this stage is where I switch to following Agile development methodology, since it is
a software problems. I developed a NodeJS sever using JavaScript and a framework called
Express.

\subsubsection{\textit{Deployment}}

I use git to deploy the application to the cloud. push the changes to git so that the system
can get the changes when made to the master branch. Tested the changes if the meet the user
needs that I define or proposed

